Optimal (Multiway) Spatial Joins

### 2024-06-01 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. Let $h$ be the full segment of $h'$. The rectangle $B_\bm{t}$ defined in \eqref{eqn:B_t} is the intersection point of $h'$ and $v$ (this point is covered by all of $r_1,...,r_{k-3}$). As $h$ is the full segment of $h'$, the point $B_\bm{t}$ must also be the intersection point of $h$ and $v$.

@@

Let $r_{k-2}$ be an arbitrary rectangle in the set $\contained_{R_{k-2}}(\bm{t})$. The definition of $\contained_{R_{k-2}}(\bm{t})$ tells us that $r_{k-2}$ covers the effective horizontal segment of $h'$ (see Section~\ref{sec:hv:type2} for the definition of an effective horizontal segment), whose right endpoint is $B_{\bm{t}}$. This means that $B_\bm{t}$ falls in $r_{k-2}$ as well.

@@

Now we know that $h \cap v \cap \bigcap_{i = 1}^{k-2} r_i$ contains $B_\bm{t}$ and is thus non-empty. Hence,
$(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J(R_1,...,R_{k-2},H,V)$. To show $(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J_2$, we still need to prove that $r_{k-2}$ covers the left endpoint of $h$. This follows immediately from the fact that $r_{k-2}$ covers the effective horizontal segment of $h'$ (which shares the same left endpoint as $h$).

@@

Denote by $p$ the intersection point of $h$ and $v$. As $h'$ is contained in $h$, to prove $h' \cap v = p$, it suffices to explain why $p$ is on $h'$. Let us represent $h$ as $[x_1,x_2] \times y$ and $p$ as $(x, y)$ for some $x \in [x_1, x_2]$. Accordingly, we can represent $h'$ as $[x_1, x_2'] \times y$ for some $x_2' \in [x_1, x_2]$. By the definition of a trimmed segment, we know that $(x_2',y)$ is the rightmost point on $h$ that falls in a left-end covering rectangle of $h$ in $R_{k-2}$. From statement (2), we have $(r_1,...,r_{k-2},h,v) \in \J_2$, meaning that $r_{k-2}$ (i) is a left-end covering rectangle of $h$, and (ii) covers $p$ ($= h \cap v$). Therefore, the x-coordinate of $p$ cannot exceed $x_2'$, allowing us to assert that $p$ is on $h'$.

>>>>

\extraspacing \underline{\em Proof of Statement (1).} Consider any tuple $\bm{t} = (r_1,...,r_{k-3}, h', v) \in \J(R_1,...,R_{k-3},H',V)$. The point $h' \cap v$ (intersection of $h'$ and $v$) is covered by all of $r_1,...,r_{k-3}$. Let $h$ be the full segment of $h'$. As $h$ contains $h'$, we must have $h \cap v = h' \cap v$.

@@

Let $r_{k-2}$ be an arbitrary rectangle in the set $\contained_{R_{k-2}}(\bm{t})$. The definition of $\contained_{R_{k-2}}(\bm{t})$ tells us that $r_{k-2}$ covers the effective horizontal segment of $\bm{t}$ (see Section~\ref{sec:hv:type2} for the definition of an effective horizontal segment), whose right endpoint is $h' \cap v$. This means that $h \cap v$ falls in $r_{k-2}$ as well.

@@

Now we know that $h \cap v \cap \bigcap_{i = 1}^{k-2} r_i$ is not empty because it equals $h' \cap v$. Hence,
$(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J(R_1,...,R_{k-2},H,V)$. To show $(r_1,...,r_{k-3}, r_{k-2}, h, v) \in \J_2$, we still need to explain why $r_{k-2}$ covers the left endpoint of $h$. This follows immediately from the fact that $r_{k-2}$ covers the effective horizontal segment of $h'$ (which shares the same left endpoint as $h$).

@@

Denote by $p$ the intersection point of $h$ and $v$. As $h'$ is contained in $h$, to prove $h' \cap v = p$, it suffices to explain why $p$ is on $h'$. Let us represent $h$ as $[x_1,x_2] \times y$ and $p$ as $(x, y)$ for some $x \in [x_1, x_2]$. Accordingly, we can represent $h'$ as $[x_1, x_2'] \times y$ for some $x_2' \in [x_1, x_2]$. By the definition of a trimmed segment, we know that $(x_2',y)$ is the rightmost point on $h$ that falls in a left-end covering rectangle of $h$ in $R_{k-2}$. From statement (2), we have $(r_1,...,r_{k-2},h,v) \in \J_2$, meaning that $r_{k-2}$ (i) is a left-end covering rectangle of $h$, and (ii) covers $p$ ($= h \cap v$). Therefore, the x-coordinate of $p$ cannot exceed $x_2'$ (i.e., $x \le x_2'$), allowing us to assert that $p$ is on $h'$.
